Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-02-12 Ben_Manuscripts/thesis/structure.tex
starting dissertation

\documentclass[journal=jpcbfk,manuscript=article]{achemso}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{xr}

\SectionNumbersOn

\externaldocument[S-]{supporting_information}

\title{Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Joseph Yelk}
\author{Matthew A. Glaser}
\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
\author{Douglas L. Gin}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\author{Xunda Feng}
\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\begin{document}

  \graphicspath{{./figures/}}

  \begin{abstract}

  %NOTE: all deleted comments are still in Draft.tex

  Periodic, nanostructured porous polymer membranes made from the cross-linked
  inverted hexagonal phase of self-assembled lyotropic liquid crystals (LLCs) are
  a promising class of materials for selective separations. In this work, we
  investigate an experimentally characterized LLC polymer membrane using
  atomistic molecular modeling. In particular, we compare simulated X-ray
  diffraction (XRD) patterns with experimental XRD data to quantify and
  understand the differences between simulation and experiment.  We find that the
  nanopores are likely composed of 5 columns of stacked LLC monomers which
  surround each hydrophilic core. Evidence suggests that these columns likely
  move independently of each other over longer time scales than accessible via
  atomistic simulation. We also find that WAXS structural features previously
  attributed to monomer tail tilt is likely instead due to ordered tail packing.
  Although this system has been reported as dry, we show that small amounts of
  water are necessary to reproduce all features from the experimental XRD pattern
  due to asymmetries introduced by hydrogen bonds between the monomer head groups
  and water molecules. Finally, we explore the composition and structure of the
  nanopores and reveal that there exists a composition gradient rather than an
  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is
  that the time scales of the dynamics are extremely long for this system,
  resulting in simulated structures that appear too ordered, thus requiring
  careful examination of the metastable states observed in order to draw any
  conclusions. The clearer picture of the nanoscopic structure of these membranes
  provided in this study will enable a better understanding of the mechanisms of
  small molecule transport within these nanopores.

  \end{abstract}

@@

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.pdf} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.38\linewidth}
                \centering
                \includegraphics[width=\textwidth]{SAXS.pdf}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D-WAXS gives details about repeating features on the
		order of angstroms. Experimentalists have explained each of the 5 major
		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
		tails are tilted with respect to the membrane plane. (R-pores) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
		from Ref.\citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
		scattering pattern is characteristic of hexagonal packing. The leading peak,
		q*, represents the distance between the d\textsubscript{100} planes, which translates 
                into a distance between pore centers of 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
  available online at \texttt{https://github.com/bencoscia/llcsim}. The python scripts used
  to simulated XRD patterns are publicly available online at \\
  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Additional details are available in 
  Section \ref{S-section:python_scripts} of the Supporting Information (SI).

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.pdf}  % Search WAXS.py for: fancy demo of r-alkanes normalization
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.pdf}  %  Search WAXS.py for: R-pi / R-double intensity measurement illustration
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.pdf} % Search WAXS.py for: Plot R-spots integrated intensity curve
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.pdf}  % 2DSAXS.py in Scripts folder 
  \caption{R-pores}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
  intensity within the region bounded by $|\mathbf{q}|$ = 1.4~$\AA^{-1}$ and 
  1.57~$\AA^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded intensities
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
  simulated spectra overlap with R-$\pi$ in those regions in all cases. (b) We
  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
  by averaging the peak heights produced by radially integrating the patterns within 
  the R-alkanes region. We took the intensity of R-spots as the average of the 
  peak intensities near 37 and 143$\degree$. (d) We measured the intensity of 
  R-pores by measuring the height of the d\textsubscript{100} peak (the leading
  peak closest to $q_r$=0) of the cross-section of the diffraction patterns along
  the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
  \end{figure}

@@

  \subsubsection{\textit{Radial Distribution Functions}}\label{method:rdfs}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \midrule
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
  \bottomrule
  \end{tabular}
  \caption{For 5 column-per-pore systems, the equilibrated vertical stacking distance, 
  $\mathit{d}_{equil}$, of monomers in the disordered basin is approximately 0.6 \AA higher than
  their initial configuration stacking distance, $\mathit{d}$, while $\mathit{d}_{equil}$ is 
  smaller than $\mathit{d}$ for disordered basin systems, but 0.9 \AA higher than experiment. 
  The correlation length is larger for systems in the ordered basin.}
  \label{table:correlation_length}
  \end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \toprule
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 4.91       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~\AA^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \bottomrule
  \end{tabular}
    \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity. In terms of 
	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $|\mathbf{q}|$
	  values that are close to experiment, while R-$\pi$ appears at a significantly lower
	  $|\mathbf{q}|$ value than experiment.\label{table:relative_intensities_300K}}
  \end{table}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.pdf}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.pdf}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
	  The maximum intensity of R-$\pi$ generated from simulations of the ordered
	  parallel displaced configuration is 3 times larger than experiment. The $q_r$
	  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between
	  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
	  the FWHM (full width at half maximum) of the simulated pattern agrees with
	  experiment within error. However the fit to the simulated data is affected by
	  the three sharp peaks which appear near $q_r$ = 0. The $q_z$ cross-sections of
	  R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits a Lorentzian profile
	  well, however the FWHM of the simulated cross-section (d) is 48\% larger than
	  the experimental cross-section (c). Additionally, the peak of the simulated
	  $q_z$ cross-section is located at a lower $q_z$ value than
	  experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

  \subsubsection*{Distance and Correlation Between Stacked Monomer Head Groups}

@@

  \subsubsection*{Shape and Intensity of the $q_r$ Cross-section of R-$\pi$}\label{section:rpi_xsection}

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental
  resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
  the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 $\AA^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccc|ccc}
  \toprule
   		                        &           \multicolumn{3}{c}{Thermal Disorder}             &             \multicolumn{3}{c}{Quenched Disorder}               \\
  \midrule
  System                        & $\sigma_x$ ($\AA$) & $\sigma_y$ (rad) & $\sigma_z$ ($\AA$) & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
  \midrule
  Ordered Sandwiched            &         0.31       &       0.33       &        0.34        &        1.48        &     0.43              &     2.30           \\
  Ordered Parallel Displaced    &         0.51       &       0.52       &        0.30        &        1.45        &     0.43              &     2.28           \\ 
  Disordered Sandwiched         &         0.41       &       0.57       &        0.32        &        1.58        &     0.43              &     2.93           \\
  Disordered Parallel Displaced &         0.39       &       0.31       &        0.33        &        1.65        &     0.43              &     2.63           \\
  \bottomrule
  \end{tabular}
  \caption{Deviation of the positions of the center of mass of head groups from their average
  positions (thermal disorder) as well as their idealized positions (quenched disorder) to use 
  as simulated disorder in our model system.}
  \label{table:quenched_disorder} 
  \end{table}

@@

  \subsubsection*{Quenched Disorder in Ensembles of Configurations}

@@

  \subsubsection*{The Implications of the New-found Understanding of R-$\pi$}

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.45\textwidth}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{nophenyls_rzplot.pdf}
  \end{subfigure}
  \caption{}\label{fig:rdouble_nophenyls}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{hbonds_tails.pdf}
  \caption{}\label{fig:hbond_visualization}
  \end{subfigure}
  \caption{(a) The structure of the head groups is responsible for the appearance of
  R-double. When we remove head groups from the trajectory, the simulated 
  diffraction pattern no longer shows R-double. (b) Monomer head groups above or below
  each other that hydrogen bond with a shared water molecule are drawn closer
  together in the $z$-direction. Blue monomers were stacked above orange monomers in the
  initial configuration.}\label{fig:hbonds}
  \end{figure}

@@

  \section*{Supporting Information}

  Detailed explanations and expansions upon the results and procedures mentioned in 
  the main text are described in the Supporting Information. This information is 
  available free of charge via the Internet at http://pubs.acs.org.

  \section*{Acknowledgements}

  J. Y. and M. A. G. were supported by the Soft Materials Research Center under NSF 
  MRSEC Grant DMR-1420736

  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

  The authors thank Richard Noble, Michael McGrath, Gregory Dwulet and Sarah Dischinger
  for useful discussions that enhanced our understanding of these LC membrane systems.

  \clearpage
  \bibliography{llc}

  \newpage

  \section*{TOC Graphic}
  \begin{figure}
  \includegraphics[width=3.25in]{new_toc_graphic.pdf}
%  \includegraphics[width=4.5cm]{toc_image_final.pdf}
%  \includegraphics[width=4.07cm]{toc_waxs.pdf}
 \end{figure}

\end{document}

% LocalWords:  Nanostructured desalination biorefinement solute RO NF bruggen
% LocalWords:  polydisperse diffusivity solutes BJC ultrafiltration nanometer
% LocalWords:  ionizable pretreatment Graphene solvated Na GA zhou resel feng
% LocalWords:  ca wt mesophases al crosslinking THF nanoporous PDMS nanopores
% LocalWords:  TODO svg eps atomistically counterion nanoscopic counterions XRD
% LocalWords:  WAXS headgroups initio metastable timescales acessible leached
% LocalWords:  SAXS alkane alkanes Antechamber bccsym molcharge QUACPAC Openeye
% LocalWords:  Gromacs berendsen timescale Packmol xyz hydrophlic xy pd tshaped
% LocalWords:  KJ NVT kJ Parrinello Rahman gmx solvate polymerization FRP FRPs
% LocalWords:  crosslink binned DC MSD subharmonic matplotlib GAFF's xrd llc ab
% LocalWords:  polarizable reconcilable screenshot crosslinked uncrosslinked AA
% LocalWords:  nanofiltration permeability interfacial diamine polysulfone der
% LocalWords:  trimesoyl immiscible polymerizes etching Osuji's nanostructured
% LocalWords:  Donnan modelling nanotubes monodispersity maruyama Zeolites Col
% LocalWords:  lyotropic thermotropic png kinetically colorbar gromacs hess dr
% LocalWords:  gimp disassociate pore's barostat racemic colorbars Nernst LLCs
% LocalWords:  entropic rzplot transitioning spoel github pymbar Yelk Glaser xr
% LocalWords:  flowback FW wastewaters wastestream fracking semipermeable TFC
% LocalWords:  solute's polymerized wijmans diffusivities amphiphilic MWCO Ia
% LocalWords:  nanostructures bicontinuous hatakeyama tortuosity Pn hII TLC ing
% LocalWords:  microstructures multilayer Xunda's refamiliarize nanostructure
% LocalWords:  nanoscale TEM LC methacrylated Eq scipy equil xz meridional phys
% LocalWords:  semiisotropic nocbar chem waxs ish fb entropically steric vv rpi
% LocalWords:  highlimit yz nematically carboxylate norestraints rb Bushey cyan
% LocalWords:  dihedrals cbar adenine carboxyl sterically QM hydroscopicity LCs
% LocalWords:  nophenyls nowater hbonds notails decorrelated Decorrelating SI
% LocalWords:  xlink uncross

>>>>

\chapter{Understanding Nanoscale Membrane Structure}\label{chapter:structure}

@@

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.pdf} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.38\linewidth}
                \centering
                \includegraphics[width=\textwidth]{SAXS.pdf}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D-WAXS gives details about repeating features on the
order of angstroms. Experimentalists have explained each of the 5 major
reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
tails are tilted with respect to the membrane plane. (R-pores) As derived from
SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
from Ref.\cite{feng_thin_2016}) The repeat spacing in the 1D-SAXS scattering
pattern is characteristic of hexagonal packing. The leading peak, q*,
represents the distance between the d\textsubscript{100} planes, which
translates into a distance between pore centers of 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
  available online at \texttt{https://github.com/bencoscia/llcsim}. The python scripts used
  to simulated XRD patterns are publicly available online at \\
  \texttt{https://github.com/joeyelk/MD-Structure-Factor}. Additional details are available in 
  Section \ref{S-section:python_scripts_structure} of the Supporting Information (SI).

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.pdf}  % Search WAXS.py for: fancy demo of r-alkanes normalization
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.pdf}  %  Search WAXS.py for: R-pi / R-double intensity measurement illustration
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.pdf} % Search WAXS.py for: Plot R-spots integrated intensity curve
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.pdf}  % 2DSAXS.py in Scripts folder 
  \caption{R-pores}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the
average intensity within the region bounded by $|\mathbf{q}|$ = 1.4~\AA$^{-1}$
and 1.57~\AA$^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded
intensities within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$,
since the simulated spectra overlap with R-$\pi$ in those regions in all cases.
(b) We measured the intensity of R-$\pi$ and R-double based on the peaks of the
$q_z$ cross-section of the diffraction pattern. (c) We measured the intensity
of R-spots by averaging the peak heights produced by radially integrating the
patterns within the R-alkanes region. We took the intensity of R-spots as the
average of the peak intensities near 37 and 143$\degree$. (d) We measured the
intensity of R-pores by measuring the height of the d\textsubscript{100} peak
(the leading peak closest to $q_r$=0) of the cross-section of the diffraction
patterns along the $q_r$ axis at $q_z$=0.
  } \label{fig:xrd_intensities}
  \end{figure}

@@

  \subsubsection{\textit{Radial Distribution Functions}}\label{method:radial_distribution_functions}

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \hline
  System             & $\mathit{d}$ (\AA) & $\mathit{d}_{equil}$ (\AA) & Correlation Length (\AA) \\
  \hline
  Sandwiched         & 3.7                &    4.27 $\pm$ 0.03         & 4.2 $\pm$ 0.8            \\
  Parallel Displaced & 3.7                &    4.33 $\pm$ 0.04         & 14.5 $\pm$ 1.3           \\ 
  Sandwiched         & 5.0                &    4.48 $\pm$ 0.07         & 3.2 $\pm$ 0.9            \\
  Parallel Displaced & 5.0                &    4.60 $\pm$ 0.08         & $<$ $d_{equil}$ \\ 
  Experiment         & --                 &    3.70                    & 9 $\pm$ 1               \\
  \hline
  \end{tabular}
  \caption{For 5 column-per-pore systems, the equilibrated vertical stacking distance, 
  $\mathit{d}_{equil}$, of monomers in the disordered basin is approximately 0.6 \AA higher than
  their initial configuration stacking distance, $\mathit{d}$, while $\mathit{d}_{equil}$ is 
  smaller than $\mathit{d}$ for disordered basin systems, but 0.9 \AA higher than experiment. 
  The correlation length is larger for systems in the ordered basin.}
  \label{table:correlation_length}
  \end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{c|ccccc}
  \hline
 		     & \multicolumn{5}{c}{Normalized Reflection Intensity}                   \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \hline
  R-alkanes  & 1.0        &  1.0       &  1.0      &  1.0       &  1.0               \\
  R-pores    & 4.91       & 49.5       & 54.0      & 50.8       & 53.4               \\
  R-spots    & 1.2        &  1.2       &  1.2      &  1.1       &  1.1               \\
  R-$\pi$    & 2.8        & 44.0       &  7.7      &  8.4       & 10.1               \\
  R-double   & 0.9        &  --        & --        &  --        & --                 \\ 
  \hline
   		     & \multicolumn{5}{c}{Reflection Location ($|\mathbf{q}|~$\AA$^{-1}$)}     \\
  \hline
             &            &            & Parallel  & Disordered & Disordered         \\
  Reflection & Experiment & Sandwiched & Displaced & Sandwiched & Parallel Displaced \\
  \hline
  R-alkanes  & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\  
  R-pores    & 0.176      &  0.170     &  0.170    & 0.173      & 0.172              \\
  R-spots    & 1.39       &  1.44      &  1.44     & 1.42       & 1.43               \\
  R-$\pi$    & 1.70       &  1.41      &  1.42     & 1.40       & 1.40               \\
  R-double   & 0.85       &  --        & --        &  --        & --                 \\ 
  \hline
  \end{tabular}
    \caption{The simulated XRD patterns of the systems tested, normalized so that
	  the average intensity of R-alkanes in each pattern equals 1, show R-pores and
	  R-$\pi$ reflections that are significantly higher than experiment and R-spots
	  reflections that are slightly lower than experiment. R-double does not appear
	  in any simulated patterns, and thus has no measurable intensity. In terms of 
	  the locations of the reflections, R-pores, R-alkanes and R-spots appear at $|\mathbf{q}|$
	  values that are close to experiment, while R-$\pi$ appears at a significantly lower
	  $|\mathbf{q}|$ value than experiment.\label{table:relative_intensities_300K}}
  \end{table}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
  \caption{FWHM = 0.792 $\pm$ 0.009 \AA$^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.pdf}
  \caption{FWHM = 0.796 $\pm$ 0.011 \AA$^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
  \caption{FWHM = 0.110 $\pm$ 0.003 \AA$^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.pdf}
  \caption{FWHM = 0.163 $\pm$ 0.011 \AA$^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
	  The maximum intensity of R-$\pi$ generated from simulations of the ordered
	  parallel displaced configuration is 3 times larger than experiment. The $q_r$
	  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between
	  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
	  the FWHM (full width at half maximum) of the simulated pattern agrees with
	  experiment within error. However the fit to the simulated data is affected by
	  the three sharp peaks which appear near $q_r$ = 0. The $q_z$ cross-sections of
	  R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits a Lorentzian profile
	  well, however the FWHM of the simulated cross-section (d) is 48\% larger than
	  the experimental cross-section (c). Additionally, the peak of the simulated
	  $q_z$ cross-section is located at a lower $q_z$ value than
	  experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

  \subsubsection{Distance and Correlation Between Stacked Monomer Head Groups}

@@

  \subsubsection{Shape and Intensity of the $q_r$ Cross-section of R-$\pi$}\label{section:rpi_xsection}

@@

  An exact quantitative comparison between the intensity and FWHM of the
  experimental and simulated cross-sections of R-$\pi$ is not feasible for
  several reasons. Experimental peaks broaden due to effects that we can not
  easily simulate such as finite size crystalline domains and instrumental
  resolution~\cite{girolami_x-ray_2016}. In our simulated XRD patterns, 
  the system size imposes limitations
  on the resolution, which makes it difficult to reliably fit peaks. This is
  especially problematic when comparing the FWHM of the $q_z$ cross-section of
  R-$\pi$, where the experimental FWHM (0.11 \AA$^{-1}$) is similar to the bin
  size in the $q_z$ direction (ca. 0.07 \AA$^{-1}$).  Additionally, we model each
  atom with a Gaussian sphere of electron density, which is a simplification.
  However, we can explore reasons for which differences in the simulation
  structure could change the peak shapes and intensities to be in better
  agreement with experiment.

@@

  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccc|ccc}
  \hline
   		                        &           \multicolumn{3}{c}{Thermal Disorder}             &             \multicolumn{3}{c}{Quenched Disorder}               \\
  \hline
  System                        & $\sigma_x$ (\AA) & $\sigma_y$ (rad) & $\sigma_z$ (\AA) & $\sigma_z$ (\AA) & $\sigma_\theta$ (rad) & $\sigma_r$ (\AA) \\
  \hline
  Ordered Sandwiched            &         0.31       &       0.33       &        0.34        &        1.48        &     0.43              &     2.30           \\
  Ordered Parallel Displaced    &         0.51       &       0.52       &        0.30        &        1.45        &     0.43              &     2.28           \\ 
  Disordered Sandwiched         &         0.41       &       0.57       &        0.32        &        1.58        &     0.43              &     2.93           \\
  Disordered Parallel Displaced &         0.39       &       0.31       &        0.33        &        1.65        &     0.43              &     2.63           \\
  \hline
  \end{tabular}
  \caption{Deviation of the positions of the center of mass of head groups from their average
  positions (thermal disorder) as well as their idealized positions (quenched disorder) to use 
  as simulated disorder in our model system.}
  \label{table:quenched_disorder} 
  \end{table}

@@

  \subsubsection{Quenched Disorder in Ensembles of Configurations}

@@

  \subsubsection{The Implications of the New-found Understanding of R-$\pi$}

@@

  \begin{figure}[!htb]
  \begin{subfigure}{0.45\textwidth}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{nophenyls_rzplot.pdf}
  \end{subfigure}
  \caption{}\label{fig:rdouble_nophenyls}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{hbonds_tails.pdf}
  \caption{}\label{fig:hbond_visualization}
  \end{subfigure}
  \caption{(a) The structure of the head groups is responsible for the appearance of
  R-double. When we remove head groups from the trajectory, the simulated 
  diffraction pattern no longer shows R-double. (b) Monomer head groups above or below
  each other that hydrogen bond with a shared water molecule are drawn closer
  together in the $z$-direction. Blue monomers were stacked above orange monomers in the
  initial configuration.}\label{fig:hydrogen_bonds}
  \end{figure}

@@
